The print method for class ranktable

### 2021-03-28 inst/ordertable_to_ranktable.Rmd
issue #43 refers

## Rank tables

Rank tables can be confusing, here is a tiny example that should
clarify things.

@@

>>>>

# Introduction

Rank tables can be confusing.  The package includes a range of
functionality for dealing with them, including a bespoke print method.
Here, I discuss two cases: firstly, a tiny toy example, and secondly
the volvo ocean racing dataset.

# Toy dataset

@@

# Volvo ocean racing dataset

(See `volvo.Rd` for more details).

```{r}
volvo_table
```

Thus we see from the first column that in leg 1, AbuDabhi came first,
Brunel third, and so on.  From the first row we see that AbuDhabi came
first in leg 1, third in leg 2, second in leg 3, and so on.  Suppose
we wish to know who came first in each leg:

```{r}
x <- wikitable_to_ranktable(volvo_table)
x
```

And we see from the first column that AbuDhabi came first in leg 1,
Brunel came first in leg 2, Dongfeng came first in leg 3, and so on.
The second column shows who came second in each leg.  Now suppose we
are interested in only the first, second and third-placed teams:

```{r}
x[,1:3]
```

The above shows that the extraction method for `ranktable` objects is
not yet written; maybe one day I will get round to implementing
`[.ranktable()` (right now I am not 100% sure that this is a good
idea).  Note that simply restoring the `ranktable` class can be
misleading:

```{r}
xx <- x[,1:3]
xx
class(xx) <- "ranktable"
xx
```

In the above, `NA`s are introduced because a `ranktable` object uses
the column names to store names of the competitors, and of course
extracting the first three columns means keeping only the first three
column names.  Observe that extraction after passing to
`ranktable_to_printable_object()` works nicely:

```{r}
ranktable_to_printable_object(x)[,1:3]
```
